---
title       : my shiny app
subtitle    : subtest
author      : rgeos
job         : savior of myself
framework   : shower        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

# Overview

|  |   |
| ---:| --- |
| **Name**> | My Shiny App - (MSA) |
| **Audience**>  | For car enthousiasts |
| **Dataset**> | `mtcars` |
| **Purpose**> | Analyze the relationship between multiple variables (**e.g.** *mpg*, *transmission*) and how are they correlated |
| **Link**> | [Try it here](https://rgeos.shinyapps.io/DataProducts/) - the link will open in a new window |

---

# Control Panel

This is a sample screen shot from the app.  
From the drop down menu choose `Miles Per Gallon` and use as predictor the `Transmission` as shown in the picture below:
![alt text][pic]

[pic]: libraries/pics/ScreenShot0.png "Screen Shot"

--- .class1  #id bg:yellow

# Main Panel

```{r echo=FALSE, eval=FALSE}
data(mtcars)
```

The application will printout a short summary of the selected variables. We will show only one of it below.

```{r}
summary(mtcars$mpg)
```

---

# Plot Panel

It will also make some plots as the box plots shown below.
```{r echo=FALSE}
boxplot(mtcars$mpg ~ mtcars$am, col = adjustcolor(palette(), alpha.f = .3), pars=list(boxwex=.5,outwex=.4))
```

---

# Plot Panel (cont)

```{r echo=FALSE}
regressionModel = function() {
  initialFit  = lm(mpg ~ ., data = mtcars)
  bestFit     = step(initialFit, trace = 0)
}
```

If you chose to show the plots for the regression model, the app will use these variables``r attr(summary(regressionModel())$terms, which = "variables")``.

Scroll down the page and you will be able to see the plots related to the regression model.

> **ENJOY**